%%==========================================================================%%
%% abstract.tex -- working abstract for the WBPET pediatric whole-body MRI   %%
%% dataset descriptor (Nature Scientific Data).                              %%
%%                                                                           %%
%% NOTE: Springer Nature requires single-file submission. Before submitting, %%
%% inline the contents of this file into main.tex (replacing \input{abstract}%%
%% with the \abstract{...} block below).                                     %%
%%==========================================================================%%

\abstract{Recently, image-based AI tools have shown great promise in a variety
of clinical applications. A key upstream task of these AI is accurate identification
of anatomy. Although several image datasets exist that can be used to build models capable 
of whole body (WB) anatomical classification, to date they have been limited to
adult images. This has hampered adoption of many AI advances in pediatric
applications, since models calibrated on adult images alone have unpredictable
performance on pediatric inputs. Besides morphological differences, state of the art WB CT 
datasets are of limited utility since MRI is prefered in pediatric imaging to ameliorate image 
related radiation doseage. What is needed therefore is a WB pediatric MRI dataset to solve the 
two entangled data paucity challenges of image coverage and aproporiate modality. 
We therefore present a 300 example pediatric WB MRI image dataset. The dataset 
spans ages 0-26 years and is comprised of both clear and various pathological presentations, 
as well as labels necessary for supervised model training.
In this manuscript, we describe the, acquisition, organization, and validation of the dataset, 
and discuss its potential to support the development and benchmarking of pediatric whole-body
anatomical analysis tools.}
