%%==========================================================================%%
%% datarecords.tex -- "Data Records". BIDS/NIfTI/sidecar boilerplate modeled  %%
%% on the reference paper, paraphrased/genericized for whole-body. REWRITE    %%
%% and verify before submission. [TBD: ...] = fill in.                        %%
%%==========================================================================%%

\section*{Data Records}\label{sec:datarecords}

% Repository + accession/DOI. OPEN: leading candidate is PhysioNet (see CLAUDE.md
% TODOs); AIMI/DOI still being resolved.
The dataset is deposited at [TBD: repository --- e.g., PhysioNet] under
[TBD: accession/DOI]. All imaging data, labels, metadata, and (where included)
radiology reports are organised as described below.

\subsection*{File organisation and naming}\label{subsec:layout}
% OPEN DECISION (to resolve): BIDS-aligned vs. custom open layout (see CLAUDE.md).
% Reusable boilerplate: BIDS establishes consistent folder structures, filename
% patterns, and formats. Caveat: BIDS is neuro-centric -> document a whole-body
% extension.
The data are organised following [TBD: the Brain Imaging Data Structure (BIDS)
standard / a custom open layout], which establishes consistent rules for folder
structure, filename patterns, and formats. [TBD: because BIDS is primarily
specified for neuroimaging, document here any whole-body-specific extensions to
the convention.] Subjects are assigned individual folders (e.g., \texttt{sub-01},
\texttt{sub-02}), each containing one or more session folders, within which the
imaging data are stored. Repeated acquisitions of the same sequence are
distinguished by a \texttt{run-} index.

\subsection*{Imaging data and sidecar metadata}\label{subsec:imaging}
% Reusable: NIfTI .nii.gz + per-scan JSON sidecars with acquisition params;
% top-level dataset_description.json + README; participants.tsv/.json; "n/a".
All imaging data are provided in NIfTI format (\texttt{.nii.gz}), each
accompanied by a sidecar JSON file containing the (de-identified) acquisition
parameters. The top-level directory includes a \texttt{dataset\_description.json}
describing the dataset and a \texttt{README} providing additional context. A
\texttt{participants.tsv} file holds per-subject demographic and clinical
information, with a companion \texttt{participants.json} defining each column and
its permitted values. Missing values are recorded as ``n/a''.

\subsection*{Machine-readable metadata and indexing}\label{subsec:metadata}
% Canonical metadata = open plain-text (TSV/CSV + JSON). OPEN: assess overlap with
% Croissant (MLCommons), which PhysioNet recommends -- adopt it rather than a
% parallel schema if it covers our needs (see CLAUDE.md).
The canonical metadata are provided as open plain-text tables (TSV/CSV) with JSON
sidecars so the dataset is fully usable with standard tooling. We aim to capture
the indexing variables useful for cohort selection and modelling, grouped as
follows (placeholder inventory --- to be finalised, and to be reconciled with the
Croissant metadata schema recommended by the target repository):

\begin{table}[h]
\caption{Candidate indexing variables provided with the dataset (placeholder).}\label{tab:vars}
\begin{tabular}{@{}ll@{}}
\toprule
Group & Example fields \\
\midrule
Subject / demographics & subject\_id, age\_at\_scan, sex, weight, height/BMI, (ethnicity) \\
Clinical / presentation & indication, normal\_vs\_abnormal, pathology\_category, region, diagnosis \\
Acquisition & scanner, field\_strength, sequence/contrast, coverage, voxel\_spacing, TR/TE \\
Labels / annotation & label\_id, anatomy, label\_type, reader\_id, reader\_experience, n\_readers \\
Reports & report\_id, scrubbed\_text, section tags, linkage to subject/scan \\
File / QC & nifti\_path, dimensions, checksum, qc\_status, license \\
\botrule
\end{tabular}
\end{table}

\subsection*{Relational index}\label{subsec:index}
% OPEN DECISION: SQLite as DERIVED convenience index (recommended) vs canonical
% store (see CLAUDE.md). Plain-text remains source of truth; SQLite generated by
% a published script.
For convenience we additionally provide a relational index (SQLite) joining
subjects, scans, labels, readers, and reports into a single queryable file. The
index is generated from the canonical plain-text tables by a published script
(Section~\ref{sec:code}), so it is fully reproducible. [TBD: describe the schema
--- tables and keys --- optionally with a schema figure.]

\subsection*{Label records}\label{subsec:labels}
Labels are stored so that provenance is explicit and queryable: each label is
keyed by target anatomy and by the annotating reader (with experience level),
and records the label type. This organisation lets users select labels by reader
or anatomy and supports the inter-reader agreement analysis in
Section~\ref{sec:validation}. [TBD: state file formats and folder location, e.g.,
under a \texttt{derivatives} folder following the same layout as the imaging.]

\subsection*{Radiology reports}\label{subsec:reports}
% NEW component: optional de-identified ("scrubbed") radiology reports paired with
% the imaging, enabling richer multimodal modelling. De-identification described
% in Methods; validated in Technical Validation.
Where available, de-identified (``scrubbed'') radiology reports are provided and
linked to the corresponding examinations, enabling richer multimodal modelling
(e.g., image--text pretraining, automated report generation, and weakly
supervised pathology labelling) beyond what imaging alone supports. The
de-identification procedure and its validation are described in
Sections~\ref{sec:methods} and~\ref{sec:validation}.
