%%==========================================================================%%
%% usagenotes.tex -- "Usage Notes".                                          %%
%% TCIA DICOM release. Access conditions TBD. DICOM tooling, CSV filtering.  %%
%% American spelling.                                                        %%
%%==========================================================================%%

\section*{Usage Notes}\label{sec:usage}

\subsection*{Access conditions}\label{subsec:license}
The dataset is hosted on The Cancer Imaging Archive (TCIA).
[TBD: state the de-identification status of the release, the resulting access model (open download versus credentialed access), the data license, expected timelines, and any restrictions on commercial use.]

\subsection*{Accessing the imaging and metadata}\label{subsec:access}
The imaging is distributed in DICOM and can be read with standard tools such as pydicom, dcm2niix, 3D Slicer, and MITK.
The accompanying plain-text metadata table (CSV) can be loaded with any standard data-analysis tooling.

\subsection*{Selecting a cohort}\label{subsec:query}
The metadata table can be filtered with standard tools (for example, pandas) to select examinations by age band, sequence or contrast, pathology category, or label availability.

\subsection*{Suggested splits, intended uses, and limitations}\label{subsec:limits}
We recommend subject-level data splits to avoid leakage across train, validation, and test partitions.
The dataset is intended for the development and benchmarking of pediatric whole-body anatomical segmentation, PET-guided lesion detection and segmentation, and cross-modality and adult-to-pediatric transfer learning.
Known limitations include the single-center origin of the cohort (Lucile Packard Children's Hospital at Stanford), heterogeneous clinical MRI protocols, a lymphoma-focused cohort with limited disease diversity, the retrospective study design, and the scope of the released labels (anatomical and tumor-lesion segmentations only, without staging labels or radiology reports).
In addition, the PET component is FDG-only and relies on MR-based attenuation correction, which can affect quantitative uptake measures.
